### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@35ed676dc3d5028bcf31c7ccadbe6861b05f6533 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@55d137a3b4bd365029a55a2fe7c121a2a01e1dbf 🚀

@@

@@

\begin{minipage}[b]{0.10\columnwidth}\raggedright

@@

@@

@@

\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright

@@

@@

\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
Cieslak et al. (2020) -- statistical interactions\strut

@@

\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
D. Chen et al. (2017) -- joint SDMs\strut

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright

@@

>>>>

\hypertarget{tbl:methods}{}

@@

\caption{\label{tbl:methods}Overview of some common graph embedding
approaches, by time of publication, alongside examples of their use in
the prediction of species interactions. Surprisingly, these methods have
not yet been used routinely to predict species interactions; most of the
examples we identified were either statistical associations, or
analogues to joint species distribution models. \(^a\): statistical
interactions; \(^b\): joint-SDM-like approach.}\tabularnewline

@@

\begin{minipage}[b]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright

@@

\endfirsthead
\begin{minipage}[b]{0.11\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright

@@

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright

@@

@@

Cieslak et al. (2020) \(^a\)\strut

@@

D. Chen et al. (2017) \(^b\)\strut

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright
GraphKKE\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
graph embedding\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
Melnyk et al. (2020)\strut
Melnyk et al. (2020) \(^a\)\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\leavevmode\hypertarget{ref-Melnyk2020GraGra}{}%
Melnyk, K., Klus, S., Montavon, G., \& Conrad, T. O. F. (2020).
GraphKKE: Graph Kernel Koopman embedding for human microbiome analysis.
\emph{Applied Network Science}, \emph{5}(1), 96.
\url{https://doi.org/10.1007/s41109-020-00339-2}
